\begin{acknowledgements}
I would have probably never been introduced to this fascinating research area had it not been for my supervisor Claudia Borg, who suggested this project in the first place.  I thank you for your advice, gentle support and for accommodating my lumbering pace - working with you was a joy.

I owe a lot of what I've learned to Gabriel Bernier-Colborne and Dmitry Ustalov; they surely went beyond what is expected out of academics, by sharing not only in-depth insight into their work, but also tangible artefacts like datasets, pre-trained embeddings and so forth.  These people are the embodiment of the idea that research - like life - is about collaboration without borders.  Also, Jose Camacho Collados and Luis Espinosa-Anke, two of the Semeval-2018, Task 9 organisers and NLP boffins, who found the time to react to the concerns and suggestions of an M.Sc. student.

Even before reading a word of this dissertation, the reader might have noticed the elegant typesetting.  This is entirely due to Jean-Paul Ebejer, who composed this fetching \LaTeX\ template and then shared the goodness with everyone else.  

Another shout out goes to Alessio Magro and Denis Cutajar, administrators of ISSA's HPC cluster: thanks for your time and patience with helping me nagivate the various issues I stumbled upon whilst trying to wrangle my experiments. 

I would also like to thank my parents and family, whose prescient gift of a ZX Spectrum back in 1986 kindled a life-long passion for computers.  Lots of love goes to my mum, who never blinked twice when her late-30's son demanded his favourite meals with the excuse that he was too busy to cook. 
 
Finally, I dedicate this work to my wife Becky whose love, unconditional support and unwavering belief in my ability to finish whatever I have started kept me motivated, even on those days when you feel like packing it in and opening a Cisk instead.
\end{acknowledgements}